### 2020-04-20 final_report/methodology.tex
Add QASS result plots

To prevent undesirable bias in results due to training set selection, all metrics
are collected in the scheme of $k$-fold cross-validation with a standard choice of
$k=5$. Herein, a sample set is subdivided into 5 disjoint folds which are
repeatedly interpreted as training and testing sets, maintaining a constant
ratio of samples between the two. In each such interpretation experiments are
repeated, and the overall value of each metric of interest is reported as the
mean across all folds.

@@

\begin{wrapfigure}{r}{0.5\textwidth}
  \vspace{-35pt}
  \begin{center}
    \includegraphics[width=0.6\textwidth]{fig4_qassplan.png}
    \caption{Schematic of QASS algorithm}
    \label{fig:qassplan}
  \end{center}
  \vspace{-20pt}
\end{wrapfigure}

We designed the Quality-Adaptive Surrogate Sampling algorithm (QASS) to iteratively increment the training set with sample points which maximise surrogate error and minimise a crowding distance metric (CDM) [6] in parameter space. On each iteration following an initial training of the surrogate on $N$ uniformly random samples, test error values were calculated according to the representative error defined in [1]. MCMC was then performed on the error function generated by performing nearest-neighbor interpolation on these test error points. The resultant samples were culled by $50\%$ according to the CDM, and then the $n$ highest-error candidates were selected for reintegration with the primary training set, beginning another training epoch. An adaptive MCMC technique [7], which tunes an ellipsoidal proposal distribution to best fit the proposal distribution, was also implemented.

Literature review:

other MC-based surrogate approaches

Smart-Sampling Algorithm [1]

Single MCMC [2]

Reverse [3][4] ASMO-PODE [5]

CDM [6]

Adaptive MCMC [7]

[1] Garud, 2016
[2] Zhou, 2018
[3] Zhang, 2020
[4] Gong, 2017

[5] Ginting, 2011
[6] Solonen, 2012
[7] Zhang, 2012

>>>>

To prevent undesirable bias in results due to training set selection, all metrics
collected in the scheme of $k$-fold cross-validation with a standard choice of
$k=5$. Herein, a sample set is subdivided into 5 disjoint folds which are
repeatedly interpreted as training and testing sets, maintaining a constant
ratio of samples between the two. In each such interpretation experiments are
repeated, and the overall value of each metric of interest is reported as the
mean across all folds.

@@

\begin{wrapfigure}{r}{0.55\textwidth}
  \vspace{-35pt}
  \begin{center}
    \includegraphics[width=0.7\textwidth]{fig4_qassplan.png}
    \caption{Schematic of QASS algorithm}
    \label{fig:qassplan}
  \end{center}
  \vspace{-80pt}
\end{wrapfigure}

We designed the Quality-Adaptive Surrogate Sampling algorithm (QASS) to iteratively increment the training/test set with sample points which maximise surrogate error and minimise a crowding distance metric (CDM) [6] in parameter space. On each iteration following an initial training of the surrogate on $N$ uniformly random samples, the surrogate was trained and AE calculated for . MCMC was then performed on the error function generated by performing nearest-neighbor interpolation on these test error points. The resultant samples were culled by $50\%$ according to the CDM, and then the $n$ highest-error candidates were selected for reintegration with the training/test set, beginning another training epoch. Validation was also performed during each iteration on independent, uniformly-random sample sets.

### 2020-04-20 final_report/results.tex
Add QASS result plots

Results

@@

>>>>

@@

Define sinusoidal toy model and justify

Explain hyperparameter tests: initsamples, stepsamples, MCMC length

\begin{figure}[h]
    \centering
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[width=1.1\linewidth]{fig5_qassincrsamp.png}
        \caption{QASS absolute training error over total sample quantity}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[width=1.1\linewidth]{fig6_qassincrtime.png}
        \caption{QASS absolute training error over number of iterations}
    \end{subfigure}
    \caption{Caption place holder}
\end{figure}

\begin{figure}[h]
  \centering
    \includegraphics[width=0.8\linewidth]{fig7_qasssampling.png}
    \caption{Absolute training error for QASS, uniform random scheme, and mixed scheme}
  \label{fig:pca}
\end{figure}
